An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-09-22 nips_2016.tex
Some cleanup to Section 5.

Our proposed test in Equation~\ref{eq:criteria} requires knowing the
distribution of the correction variable $X_{\rm corr}$ such that $X_{\rm norm} +
X_{\rm corr} = X_{\rm log}$, where $X_{\rm norm} \sim \mathcal{N}(0,\sigma^2)$
and $X_{\rm log}$ has a standard logistic CDF, $(1+\exp(-X))^{-1}$. In
Section~\ref{sec:analysis}, we show that the accuracy of the test depends on the
absolute error between the CDFs of $X_{\rm norm} + X_{\rm corr}$ and $X_{\rm
log}$. Consequently, we need to minimize this in our construction of $X_{\rm
corr}$. More formally, let $\Phi_\sigma(X) = \Phi(X/\sigma)$ where $\Phi$ is the
standard normal CDF\footnote{Hence, $\Phi_\sigma$ is the CDF of a zero-mean
Gaussian with variance $\sigma$.}, $S(X)$ be the logistic function, and
$C_{\sigma}(X)$ be the \emph{density} of the correction $X_{\rm corr}$
distribution. Our goal, based on Equation~\ref{eq:deconvolution}, is to solve
the following optimization problem:
\begin{equation}\label{eq:overall_corr_problem}
    C_\sigma^* = \argmin_{C_\sigma} |\Phi_{\sigma} * C_{\sigma} - S|
\end{equation}
where $*$ denotes convolution. {\color{blue} Daniel: This is very unusual use of
convolutions (i.e., CDF * DENSITY = CDF). It's valid but I was very surprised to
know that.} For computation of $C_\sigma$, we assume that its input $Y$ and
another variable $X$ lie in the intervals $[-V,V]$ and $[-2V,2V]$, respectively.
{\color{blue} Daniel: I am a little confused at the different interval sizes.}
In continuous form, the optimization problem is therefore
\begin{equation}\label{eq:conv1}
    C_\sigma^* = \argmin_{C\sigma} \; \sup_{x \in [-2V,2V]}\left|\int_{-V}^{V}\Phi_{\sigma}(x-y) C_{\sigma}(y)dy - S(x)\right|
\end{equation}
To get $C_\sigma^*$ in a practical form, we discretize $X$ and $Y$ into $4N+1$
and $2N+1$ values respectively. Writing $X_i = i*V/N$ and $Y_j = j*V/N$, the
condition in Equation~\ref{eq:conv1} can be re-expressed as:
\begin{equation}\label{eq:conv2}
    C_\sigma^* = \argmin_{C_\sigma} \max_{i \in \{-2N,\ldots,2N\}}\left|\sum_{j = -N}^{N}\Phi_{\sigma}(X_i-Y_j) C_{\sigma}(Y_j) - S(X_i)\right|.
\end{equation}
Defining a matrix $M$ and vectors $u$ and $v$ such that $M_{ij} =
\Phi_{\sigma}(X_i-Y_j)$, $u_j = C_{\sigma}(Y_j)$, and $v_i = S(X_i)$,
Equation~\ref{eq:conv2} is equivalent to minimizing the $L_1$ norm:
\begin{equation}\label{eq:optimization_l1}
    u^* = \argmin_{u} \|Mu-v\|_1.
\end{equation}
{\color{blue} Daniel: Equation~\ref{eq:optimization_l1} is finding
the $C_\sigma$ minimizing the $L_1$ norm, but the previous one,
Equation~\ref{eq:conv2}, is finding the $C_\sigma$ that is minimizing the
$L_\infty$ norm, i.e., the maximum value! If we want this to be the $L_1$ norm
(and I think we do) then Equation~\ref{eq:conv2} needs an outer sum over the $i$
terms. In addition, Equation~\ref{eq:conv1} also needs to be modified, perhaps
eliminate the ``sup'' but keep $x \in [-2V,2V]$}

@@

\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\begin{algorithm}[t]
\Input{Number of samples $T$, minibatch size $m$, error bound $\delta$, pre-computed correction $C_1(X)$ distribution, initial sample $\theta_1$.}
\Output{A chain of $T$ samples $\{\theta_1, \ldots, \theta_T\}$ from $p(\theta)$\;}
\For{$t=\{1, \ldots, T\}$}{
    Propose a candidate $\theta'$\ from proposal distribution $q(\theta'\mid\theta_t)$\;
    Draw a minibatch of $m$ points $x_i$, compute $\Delta^*(\theta_t,\theta')$ and sample variance $\sigma^2(\Delta^*)$\;
    Estimate moments $E|\Lambda_i-\Lambda|$ and $E|\Lambda_i-\Lambda|^3$ from the sample, and error $\epsilon$ from equation (\ref{eq:clt-bounds3})\;
    \While {$\sigma^2(\Delta^*) \ge 1$ {\bf or} $\epsilon > \delta$}{
    	Draw $m$ more samples to augment the minibatch, update $\Delta^*$, $\sigma^2(\Delta^*)$ and $\epsilon$ estimates\;
    }
    Draw $X_{\rm norm} \sim \mathcal{N}(0,1-\sigma^2(\Delta*))$ and
    $X_{\rm corr}$ from the correction distribution $C_1(X)$\;

@@

We now derive error bounds for our M-H test, and for the approximate target
distribution that it generates. From Section~\ref{sec:correction}, we know that
it is possible to generate the correction samples $X_{\rm corr}$ with a CDF
error of at most single-precision floating point error, and possibly better. We
therefore treat the $X_{\rm corr}$ variable as a sample from the exact
correction distribution and we will not analyze its errors.

In the most similar prior works, \cite{cutting_mh_2014} uses asymptotic arguments based
on the central limit theorem to argue that its approximate acceptance test error tends to
zero as batch size increases. But no quantitative bounds are given. In
\cite{icml2014c1_bardenet14}, explicit bounds are given, but they depend on a bound on
the quantity:
\begin{equation}
  \max_{1\leq i\leq N}|\log p(x_i|\theta') - \log p(x_i|\theta)|
\end{equation}
while such bounds can be derived easily for simple models, its unclear how to derive them
for a complex model such as a neural network.

In this paper, we rely on quantitave forms of the central limit theorem which rely on measurable
statistics from the minibatch $\{x_i\}$. Thus a sampler using our approach does not need to ``see''
data beyond the current minibatch. This supports use of the sampler on very large datasets, and
in online mode where the dataset is presented as a stream.

The outline of this section is as follows: we first present bounds on the absolute
and relative error (in CDF) of the distribution of $\Delta^*$ vs a Normal distribution. We then show that
these errors bounds are preserved after the addition of other random variables, in particular
$X_{\rm norm}$ and $X_{\rm corr}$. From this it follows that the acceptance test has the same error bound.

The quantitative central-limit result below comes from \cite{explicit-clt05}:

\begin{lemma}\label{lem:quant_clt}
Let $X_1,\ldots,X_n$ be
a set of zero-mean, independent, identically-distributed random variables with sample mean $\hat{X}$ and
variance $\sigma^2(\hat{X})$ where:
\begin{equation}
    \hat{X} = \frac{1}{n}\sum_{i=1}^nX_i \qquad {\rm and} \qquad \sigma(\hat{X}) = \frac{1}{n}\left(\sum_{i=1}^n(X_i-\hat{X})^2\right)^{\frac{1}{2}}
\end{equation}
then $t=\hat{X}/\sigma(\hat{X})$ has an approximate Student's distribution which approaches a normal
distribution in the limit. Then from~\cite{explicit-clt05}:
\begin{equation}\label{eq:clt-bounds}
    \sup_x|{\rm Pr}(t<x) - \Phi(x)| \leq \frac{6.4E|X|^3+2E|X|}{\sqrt{n}}
\end{equation}
\end{lemma}

So as long as we know the first and third absolute moments $E|X|$ and $E|X|^3$, we can bound the
error of the normal approximation, which decays as $O(n^{-\frac{1}{2}})$. Making the change of variables
$y = x \sigma(\hat{X})$, Equation~\ref{eq:clt-bounds} becomes
\begin{equation}\label{eq:clt-bounds2}
   \sup_y\left|{\rm Pr}(\hat{X}< y) - \Phi\left(\frac{y}{\sigma(\hat{X})}\right)\right| \leq \frac{6.4E|X|^3+2E|X|}{\sqrt{n}}
\end{equation}
which shows that the distribution of $\hat{X}$ approaches the normal distribution $\mathcal{N}(0,\sigma^2(\hat{X}))$
whose variance is $\sigma^2(\hat{X})$, measured from the sample.

To apply this to our test, let $X_i = \Lambda_i(\theta,\theta') - \Lambda(\theta,\theta')$,
then the $X_i$ are zero-mean, IID variables.
Take $n=b$ the minibatch size, and then:
\begin{equation}
    \hat{X} = \Delta^*(\theta,\theta') - \Delta(\theta,\theta') 
\end{equation}
so that $\sigma(\hat{X}) = \sigma(\Delta^*)$.
\begin{corollary}
We can now substitute into Equation~\ref{eq:clt-bounds2} and displace by the mean, giving:
\begin{equation}\label{eq:clt-bounds3}
    \sup_y\left|{\rm Pr}(\Delta^*< y) - \Phi\left(\frac{y-\Delta}{\sigma(\Delta^*)}\right)\right| \leq \frac{6.4E|X|^3+2E|X|}{\sqrt{b}} = \epsilon(\theta,\theta',b)
\end{equation}
\end{corollary}

We have shown that the distribution of $\Delta^*$ approximates a Normal
distribution with mean $\Delta$ and variance $\sigma^2(\Delta^*)$, and bounded
its error with estimable quantities. Both $E|X|$ and $E|X|^3$ can be estimated
as means of $|\Lambda_i - \Lambda|$ and $|\Lambda_i - \Lambda|^3$ respectively
on each minibatch. We expect this will often be accurate enough on minibatches
with hundreds or thousands of points, but otherwise bootstrap CIs can be
computed from those sequences. Since the bounds are monotone in $E|X|$ and
$E|X|^3$, using upper bootstrap CI limits will provide high-confidence error
bounds.

{\color{blue} Daniel: TODO provide a better transition for this paragraph.}

@@

\begin{corollary}
If $\sup_y|{\rm Pr}(\Delta^* < y) - \Phi(\frac{y-\Delta}{\sigma(\Delta^*)})|
\leq \epsilon(\theta,\theta',b)$, then
\begin{equation}
    \sup_y|{\rm Pr}(\Delta^*+X_{\rm norm}+X_{\rm corr} < y) - S(y-\Delta)| \leq \epsilon(\theta,\theta',b)
\end{equation}
where $S(x)$ is the standard logistic function, and $X_{\rm norm}$ and $X_{\rm corr}$ are generated as per Algorithm 1. 
\end{corollary}

\begin{proof}
We apply Lemma~\ref{lem:cdf_bounds} twice. First take:
\begin{equation}
    P(y) = Pr(\Delta^* < y) \qquad {\rm and}\qquad Q(y) = \Phi\left(\frac{y-\Delta}{\sigma(\Delta^*)}\right)
\end{equation}
and convolve with the distribution of $X_n$ which has density $\phi(X/\sigma_n)$
where $\sigma_n^2 = 1 - \sigma^2(\Delta^*)$. This yields the next iteration of
$P$ and $Q$
\begin{equation}
    P'(y) = Pr(\Delta^*+X_{\rm norm} < y) \qquad {\rm and}\qquad Q'(y) = \Phi\left({y-\Delta}\right)
\end{equation}
Now we convolve with the distribution of $X_{\rm corr}$ which gives:
\begin{equation}
    P''(y) = Pr(\Delta^*+X_{\rm norm}+X_{\rm corr} < y) \qquad {\rm and}\qquad Q''(y) = S\left({y-\Delta}\right)
\end{equation}
Both steps preserve the error bound $\epsilon(\theta,\theta',b)$. Finally
$S(y-\Delta)$ is a logistic CDF centered at $\Delta$, and so $S(y-\Delta) = {\rm
Pr}(\Delta + X_{\rm log} < y)$ for a logistic random $X_{\rm log}$. We conclude
that the probability of acceptance for the actual test ${\rm Pr}(\Delta^*+X_{\rm
norm}+X_{\rm corr} > 0)$ differs from the exact test ${\rm Pr}(\Delta+X_{\rm
log} > 0)$ by at most $\epsilon$.
\end{proof}

In fact we can do better than this approximation (showing the error decreases as $O(n^{-1})$) by using a more
precise limit distribution under an additional assumption. Let $\mu_i$ denote the $i^{th}$ moment, and $b_i$
denote the $i^{th}$ absolute moment of $X$. If Cramer's condition holds, i.e. if
\begin{equation}
  \lim_{t \to \infty} \sup |E(\exp(i t X))| < 1.
\end{equation}

Equation 2.2 in Bentkus et al.'s work on Edgeworth expansions~\cite{Bentkus97}
provides the following:

@@

We conduct two sets of experiments to explore the benefits of our minibatch MH test and to
benchmark it with previous work. In Section~\ref{ssec:gaussians}, we show that our test enables
samples to converge to the posterior distribution of a heated Gaussian mixture model. In
Section~\ref{ssec:logistic}, we analyze its efficiency on logistic regression. 
%In %Section~\ref{ssec:nets}, we apply the test for deep learning. 
Appendices~\ref{app:gaussian},~\ref{app:logistic} %and~\ref{app:nnet} 
contain more detailed information on these respective experiments.

>>>>

Our proposed test in Equation~\ref{eq:criteria} requires knowing the
distribution of the correction variable $X_{\rm corr}$ such that $X_{\rm norm} +
X_{\rm corr} = X_{\rm log}$, where $X_{\rm norm} \sim \mathcal{N}(0,\sigma^2)$
and $X_{\rm log}$ has a standard logistic CDF, $(1+\exp(-X))^{-1}$. In
Section~\ref{sec:analysis}, we show that the accuracy of the test depends on the
absolute error between the CDFs of $X_{\rm norm} + X_{\rm corr}$ and $X_{\rm
log}$. Consequently, we need to minimize this in our construction of $X_{\rm
corr}$. More formally, let $\Phi_\sigma(X) = \Phi(X/\sigma)$ where $\Phi$ is the
standard normal CDF\footnote{Hence, $\Phi_\sigma$ is the CDF of a zero-mean
Gaussian with variance $\sigma$.}, $S(X)$ be the logistic function, and
$C_{\sigma}(X)$ be the \emph{density} of the correction $X_{\rm corr}$
distribution. Our goal, based on Equation~\ref{eq:deconvolution}, is to solve
the following optimization problem:
\begin{equation}\label{eq:overall_corr_problem}
    C_\sigma^* = \argmin_{C_\sigma} |\Phi_{\sigma} * C_{\sigma} - S|
\end{equation}
where $*$ denotes convolution. {\color{blue} Daniel: This is very unusual use of
convolutions (i.e., CDF * DENSITY = CDF). It's valid but I was very surprised to
know that.} For computation of $C_\sigma$, we assume that its input $Y$ and
another variable $X$ lie in the intervals $[-V,V]$ and $[-2V,2V]$, respectively.
{\color{blue} Daniel: I am a little confused at the different interval sizes.}
In continuous form, the optimization problem is therefore
\begin{equation}\label{eq:conv1}
    C_\sigma^* = \argmin_{C\sigma} \; \sup_{x \in [-2V,2V]}\left|\int_{-V}^{V}\Phi_{\sigma}(x-y) C_{\sigma}(y)dy - S(x)\right|
\end{equation}
To get $C_\sigma^*$ in a practical form, we discretize $X$ and $Y$ into $4N+1$
and $2N+1$ values respectively. If $i \in \{-2N, \ldots, 2N\}$ and $j \in \{-N,
\ldots, N\}$, then we can write $X_i = i(V/N)$ and $Y_j = j(V/N)$, and the
condition in Equation~\ref{eq:conv1} can be re-expressed as:
\begin{equation}\label{eq:conv2}
    C_\sigma^* = \argmin_{C_\sigma} \max_{i \in \{-2N,\ldots,2N\}}\left|\sum_{j = -N}^{N}\Phi_{\sigma}(X_i-Y_j) C_{\sigma}(Y_j) - S(X_i)\right|.
\end{equation}
To make the problem easier to understand, we can define a matrix $M$ and vectors
$u$ and $v$ such that $M_{ij} = \Phi_{\sigma}(X_i-Y_j)$, $u_j =
C_{\sigma}(Y_j)$, and $v_i = S(X_i)$, where the indices $i$ and $j$ are
appropriately translated to be non-negative indices for $M, u,$ and $v$. Thus,
Equation~\ref{eq:conv2} is equivalent to minimizing the $L_1$ norm:
\begin{equation}\label{eq:optimization_l1}
    u^* = \argmin_{u} \|Mu-v\|_1.
\end{equation}
{\color{blue} Daniel: Equation~\ref{eq:optimization_l1} is finding
the $C_\sigma$ minimizing the $L_1$ norm, but the previous one,
Equation~\ref{eq:conv2}, is finding the $C_\sigma$ that is minimizing the
$L_\infty$ norm, i.e., the maximum value! If we want this to be the $L_1$ norm
(and I think we do) then Equation~\ref{eq:conv2} needs an outer sum over the $i$
terms. In addition, Equation~\ref{eq:conv1} also needs to be modified, perhaps
eliminate the ``sup'' but keep $x \in [-2V,2V]$}

@@

\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\begin{algorithm}[t]
\Input{Number of samples $T$, minibatch size $m$, error bound $\delta$, pre-computed correction $C_1(X)$ distribution, initial sample $\theta_1$.}
\Output{A chain of $T$ samples $\{\theta_1, \ldots, \theta_T\}$ from $p(\theta)$\;}
\For{$t=\{1, \ldots, T\}$}{
    Propose a candidate $\theta'$\ from proposal distribution $q(\theta'\mid\theta_t)$\;
    Draw a minibatch of $m$ points $x_i$, compute $\Delta^*(\theta_t,\theta')$ and sample variance $\sigma^2(\Delta^*)$\;
    Estimate moments $E|\Lambda_i-\Lambda|$ and $E|\Lambda_i-\Lambda|^3$ from the sample, and error $\epsilon$ from equation (\ref{eq:clt-bounds3})\;
    \While {$\sigma^2(\Delta^*) \ge 1$ {\bf or} $\epsilon > \delta$}{
    	Draw $m$ more samples to augment the minibatch, update $\Delta^*$, $\sigma^2(\Delta^*)$ and $\epsilon$ estimates\;
    }
    Draw $X_{\rm norm} \sim \mathcal{N}(0,1-\sigma^2(\Delta^*))$ and
    $X_{\rm corr}$ from the correction distribution $C_1(X)$\;

@@

We now derive error bounds for our M-H test, and for the approximate target
distribution that it generates. From Section~\ref{sec:correction}, we know that
it is possible to generate the correction samples $X_{\rm corr}$ with a CDF
error of at most single-precision floating point error, and possibly better
{\color{blue} (Daniel: I can fix this to cite Table~\ref{tab:xcorr}'s values,
that will probably be better.)}. We therefore treat the $X_{\rm corr}$ variable
as a sample from the exact correction distribution and we will not analyze its
errors.

In the most similar prior works,~\cite{cutting_mh_2014} uses asymptotic
arguments based on the Central Limit Theorem to argue that its approximate
acceptance test error tends to zero as batch size increases. But no quantitative
bounds are given. In~\cite{icml2014c1_bardenet14}, explicit bounds are given,
but they depend on bounding
\begin{equation}\label{eq:bad_bound}
    C_{\theta, \theta'} = \max_{1\leq i\leq N}|\log p(x_i\mid\theta') - \log p(x_i\mid\theta)|.
\end{equation}
Such bounds can be derived efficiently for models such as logistic regression,
but it is unclear how to derive them for a complex model such as a neural
network. In general, since we obtain a new $\theta'$ value each iteration, one
would need to iterate through all the $p(x_i\mid \theta')$ terms, defeating the
purpose of minibatch MCMC.

In this paper, we use quantitative forms of the Central Limit Theorem which rely
on measurable statistics from a single minibatch. Thus a sampler using our
approach does not need to ``see'' data beyond the current minibatch. This
supports use of the sampler on very large datasets, and in online mode where the
dataset is presented as a stream.

For the analysis, in Section~\ref{ssec:delta_star_distribution}, we first
present bounds on the absolute and relative error (in terms of the CDFs) of the
distribution of $\Delta^*$ vs a Gaussian. We then show in
Section~\ref{ssec:preserve_bounds} that these error bounds are preserved after
the addition of other random variables, in particular $X_{\rm norm}$ and $X_{\rm
corr}$. From this it follows that the acceptance test has the same error bound.

\subsection{Bounding the Distribution of $\Delta^*$ Versus a Gaussian}\label{ssec:delta_star_distribution}

To start, we use the following quantitative central-limit result (from
\cite{explicit-clt05}):

\begin{lemma}\label{lem:quant_clt}
Let $X_1,\ldots,X_n$ be a set of zero-mean, independent, identically-distributed
random variables with sample mean $\hat{X}$ and variance $\sigma^2(\hat{X})$
where:
\begin{equation}
    \hat{X} = \frac{1}{n}\sum_{i=1}^nX_i \qquad {\rm and} \qquad \sigma(\hat{X}) = \frac{1}{n}\left(\sum_{i=1}^n(X_i-\hat{X})^2\right)^{\frac{1}{2}}.
\end{equation}
This means $t=\hat{X}/\sigma(\hat{X})$ has an approximate Student's distribution
which approaches a normal distribution in the limit. Then
from~\cite{explicit-clt05}:
\begin{equation}\label{eq:clt-bounds}
    \sup_x|{\rm Pr}(t<x) - \Phi(x)| \leq \frac{6.4E|X|^3+2E|X|}{\sqrt{n}}.
\end{equation}
\end{lemma}

{\color{blue} Daniel: the notation here was (and still is, to a lesser extent)
the source of considerable confusion for me. Do we want $\sigma(X)$ or
$\sigma(\hat{X})$? I think in Lemma~\ref{lem:quant_clt} we want the former, not
the latter. OH ALSO, this section uses $n$ as the full data size, which means
before this section, we should use $n$, not $N$, for the full data size, right?
The Bardenet paper uses $n$ to represent the full data size.}

Lemma~\ref{lem:quant_clt} demonstrates that as long as we know the first and
third absolute moments $E|X|$ and $E|X|^3$, we can bound the error of the normal
approximation, which decays as $O(n^{-\frac{1}{2}})$. Making the change of
variables $y = x \sigma(\hat{X})$, Equation~\ref{eq:clt-bounds} becomes
\begin{equation}\label{eq:clt-bounds2}
   \sup_y\left|{\rm Pr}(\hat{X}< y) - \Phi\left(\frac{y}{\sigma(\hat{X})}\right)\right| \leq \frac{6.4E|X|^3+2E|X|}{\sqrt{n}},
\end{equation}
showing that the distribution of $\hat{X}$ approaches the normal distribution
$\mathcal{N}(0,\sigma^2(\hat{X}))$ whose variance is $\sigma^2(\hat{X})$,
measured from the sample.

To apply this to our test, let $X_i = \Lambda_i(\theta,\theta') -
\Lambda(\theta,\theta')$, so that the $X_i$ are zero-mean, i.i.d. variables. If
instead of all $n$ samples, we only extract a subset of $b$ samples
corresponding to our minibatch, we can connect $\hat{X}$ with our $\Delta^*$
term:
\begin{equation}\label{eq:x-hat}
    \hat{X} = \Delta^*(\theta,\theta') - \Delta(\theta,\theta'),
\end{equation}
so that $\sigma(\hat{X}) = \sigma(\Delta^*)$. This results in the following
Corollary:

\begin{corollary}\label{cor:our_bound_delta_prime}
We can now substitute into Equation~\ref{eq:clt-bounds2} and displace by the mean, giving:
\begin{equation}\label{eq:clt-bounds3}
    \sup_y\left|{\rm Pr}(\Delta^*< y) - \Phi\left(\frac{y-\Delta}{\sigma(\Delta^*)}\right)\right| \leq \frac{6.4E|X|^3+2E|X|}{\sqrt{b}} = \epsilon(\theta,\theta',b)
\end{equation}
\end{corollary}

Corollary~\ref{cor:our_bound_delta_prime} shows that the distribution of
$\Delta^*$ approximates a Normal distribution with mean $\Delta$ and variance
$\sigma^2(\Delta^*)$. Furthermore, it bounds the error with \emph{estimable
quantities}: both $E|X|$ and $E|X|^3$ can be determined as means of $|\Lambda_i
- \Lambda|$ and $|\Lambda_i - \Lambda|^3$, respectively, on each minibatch. We
expect this will often be accurate enough on minibatches with hundreds or
thousands of points, but otherwise bootstrap CIs can be computed from those
sequences. Since the bounds are monotone in $E|X|$ and $E|X|^3$, using upper
bootstrap CI limits will provide high-confidence error bounds.

\subsection{Bounds are Preserved After Adding Random Variables}\label{ssec:preserve_bounds}

We next relate the CDFs of distributions and show that bounds are preserved
after adding random variables.

@@

Relating Lemma~\ref{lem:cdf_bounds} to our acceptance test, we observe that:

\begin{corollary}\label{cor:bounds_preserved}
If $\sup_y|{\rm Pr}(\Delta^* < y) - \Phi(\frac{y-\Delta}{\sigma(\Delta^*)})|
\leq \epsilon(\theta,\theta',b)$, then
\begin{equation}
    \sup_y|{\rm Pr}(\Delta^*+X_{\rm norm}+X_{\rm corr} < y) - S(y-\Delta)| \leq \epsilon(\theta,\theta',b)
\end{equation}
where $S(x)$ is the standard logistic function, and $X_{\rm norm}$ and $X_{\rm corr}$ are generated as per Algorithm 1. 
\end{corollary}

\begin{proof}
We apply Lemma~\ref{lem:cdf_bounds} twice. First take:
\begin{equation}
    P(y) = {\rm Pr}(\Delta^* < y) \qquad {\rm and}\qquad Q(y) = \Phi\left(\frac{y-\Delta}{\sigma(\Delta^*)}\right)
\end{equation}
and convolve with the distribution of $X_n$ which has density $\phi(X/\sigma_n)$
where $\sigma_n^2 = 1 - \sigma^2(\Delta^*)$. This yields the next iteration of
$P$ and $Q$
\begin{equation}
    P'(y) = {\rm Pr}(\Delta^*+X_{\rm norm} < y) \qquad {\rm and}\qquad Q'(y) = \Phi\left({y-\Delta}\right)
\end{equation}
Now we convolve with the distribution of $X_{\rm corr}$ which gives:
\begin{equation}
    P''(y) = {\rm Pr}(\Delta^*+X_{\rm norm}+X_{\rm corr} < y) \qquad {\rm and}\qquad Q''(y) = S\left({y-\Delta}\right)
\end{equation}
Both steps preserve the error bound $\epsilon(\theta,\theta',b)$. Finally
$S(y-\Delta)$ is a logistic CDF centered at $\Delta$, and so $S(y-\Delta) = {\rm
Pr}(\Delta + X_{\rm log} < y)$ for a logistic random $X_{\rm log}$. We conclude
that the probability of acceptance for the actual test ${\rm Pr}(\Delta^*+X_{\rm
norm}+X_{\rm corr} > 0)$ differs from the exact test ${\rm Pr}(\Delta+X_{\rm
log} > 0)$ by at most $\epsilon$.
\end{proof}

As our discussion in Section~\ref{sec:our_algorithm} showed, as the distribution
of $\Delta^*$ approaches a Gaussian, our new MH test becomes more accurate.
Corollary~\ref{cor:bounds_preserved} shows that the bounds from
Section~\ref{ssec:delta_star_distribution} are preserved after the addition of
the random variables we use, showing that our test should remain accurate.

{\color{blue} Daniel: Do we want to include this new analysis? There seem to be
two different ways we show the bound. The first part (above) is nice and I like
it (and it seems to show all we need for Algorithm 1, doesn't it?}

In fact we can do better than this approximation (showing the error decreases as
$O(n^{-1})$) by using a more precise limit distribution under an additional
assumption. Let $\mu_i$ denote the $i^{th}$ moment, and $b_i$ denote the
$i^{th}$ absolute moment of $X$. If Cramer's condition holds:
\begin{equation}\label{eq:cramers_condition}
    \lim_{t \to \infty} \sup |E(\exp(i t X))| < 1,
\end{equation}
then Equation 2.2 in Bentkus et al.'s work on Edgeworth
expansions~\cite{Bentkus97} provides the following Lemma:

@@

We conduct two sets of experiments to explore the benefits of our minibatch MH
test and to benchmark it with previous work. In Section~\ref{ssec:gaussians}, we
show that our test enables samples to converge to the posterior distribution of
a heated Gaussian mixture model. In Section~\ref{ssec:logistic}, we analyze its
efficiency on logistic regression.  Appendices~\ref{app:gaussian}
and~\ref{app:logistic} contain more detailed information on these respective
experiments.
